Object-Oriented Internet - Azure Interoperability

### 2020-11-07 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- created Markdown/60.GatewayImplementation.md

\keywords{Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture}

>>>>

\keywords{ Azure, Cloud Computing, Object-Oriented Internet, Industrial communication, Industry 4.0, Internet of Things, Machine to Machine Communication, OPC Unified Architecture,
           Reactive Networking (RxNetworking)  }
